Twists of supersymmetric gauge theories

### 2019-11-08 paper.tex

\subsection{Dimension 7}

% \cN=1 SYM, three twists identical to dimension 8

>>>>

\subsection{Dimension 7}
The 7-dimensional $\mc N=1$ super Yang-Mills theory is obtained by dimensional reduction of $\mc N=1$ super Yang-Mills from $\RR^{10}$ to $\RR^7$.  It has BRST fields given by a ghost, a 7d gauge field $A$, three $\gg$-valued scalar fields $\phi_1$, $\phi_2$ and $\phi_3$, and a symplectic Dirac spinor field $\lambda$ in $S \otimes W$, where $W$ is a 2-dimensional symplectic vector space.

In 7 dimensions, exactly like in 8-dimensions, there are 3 classes of inequivalent non-zero supercharges by which we can twist.
\begin{enumerate}
 \item Rank 1 pure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)=0$.  Such supercharges are minimal: they have 4-dimensional image in $\CC^7$.
 \item Rank 1 impure spinors, i.e. elements $Q = \alpha \otimes w \in S \otimes W$ where $(\alpha, \alpha)\ne 0$.  Such supercharges are topological.
 \item Rank 2 square-zero spinors, i.e. square-zero elements of the form $Q = \alpha_1 \otimes w_1 + \alpha_2 \otimes w_2$, where $w_1$ and $w_2$ are linearly independent.  Such supercharges have a 5-dimensional image in $\CC^7$.  Twists by such supercharges are still only $\ZZ/2\ZZ$-graded. 
\end{enumerate}

The three twists of 7-dimensional $\mc N=1$ super Yang-Mills theory can be calculated by dimensionally reducing the twists of 8-dimensional super Yang-Mills.

\begin{theorem} \label{7d_holo_twist_thm}
The minimal twist of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau 3-fold $X_3$ and an oriented 1-manifold $L$ is equivalent to mixed BF theory on the product $X_3 \times L_{\mr{dR}}$. This twist degenerates to a one-parameter family of topological twists of the form $\map(X_3 \times L_{\mr{dR}}, B\gg)_{\mr{Hod}}$.
\end{theorem}

\begin{proof}

\end{proof}

\begin{theorem} \label{7d_rank2_twist_thm}
The twist by a rank 2 supercharge of 7d $\mc N=1$ super Yang-Mills theory on the product of a Calabi-Yau surface $X_2$ with an oriented 3-manifold $M_3$ is equivalent to mixed Chern-Simons theory on $X_2 \times (M_3)_{\mr{dR}}$. \chris{actually I need to think about the twisting homomorphism here.}
\end{theorem}

\begin{proof}

\end{proof}
